---
title: "Weight of Fish"
author: "Anthony Benitez"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight


## Perch

```{r}
Fish <- read.csv("Fish.csv")
perch <- filter(Fish, Species == "Perch")
```

```{r}
perch <- select(perch,-Species)
```

### Best Models


### Best Two regressor model
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```
The best two regressor model is height and weight because those are the highest adjusted r squared.

```{r}
perchmodel <- lm(Weight ~ Height + Width, data = perch)
summary.lm(perchmodel)
```

```{r}
pmodel <- lm(Weight ~ Height + Width + Length1 + Length2 + Length3, data = perch)
summary.lm(pmodel)
```
We used two models to figure out our Residual standard error and the adjusted r squared of both models for the first residual it is 85.17 then the second one is 87.11 for the adjusted r squared the first one is 0.94 then the second on it is 0.9372.



## Bream
```{r}
Fish <- read.csv("Fish.csv")
Bream <- filter(Fish, Species == "Bream")
```

```{r}
Bream <- select(Bream,-Species)
```
### Best Models

### Best Two regressor model
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Bream,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The best regression model is Length1 Height and Weight because it is at the top.

```{r}
Breammodel <- lm(Weight ~ Height + Width, data = Bream)
summary.lm(Breammodel)
```

```{r}
Bmodel <- lm(Weight ~ Height + Width + Length1 + Length2 + Length3, data = Bream)
summary.lm(Bmodel)
```

The first Residual standard error 53.98 the second one 53.96 the first adjusted r square is 0.9334 the adjusted r square is 0.9335



## Roach
```{r}
Fish <- read.csv("Fish.csv")
Roach <- filter(Fish, Species == "Roach")
```

```{r}
Roach <- select(Roach,-Species)
```
### Best Models

### Best Two regressor model
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

```{r}
Roachmodel <- lm(Weight ~ Height + Width, data = Roach)
summary.lm(Roachmodel)
```

```{r}
Rmodel <- lm(Weight ~ Height + Width + Length1 + Length2 + Length3, data = Roach)
summary.lm(Rmodel)
```

The first Residual standard error is 35.63 the second is 37.58 the first adjusted r square is 0.8391 the second one is 0.821.


## Final Summary Statements


In all the test we did it showed us that for the first model the first summary was the best for the second model the second summary was the best and for the third model the first summary was the best all the summarys were focused on finding which fish weighed the most and how would we be able to mesusre it by. 
