---
title: "Weight of Fish"
author: "Anthony Benitez"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight


## Perch

```{r}
Fish <- read.csv("Fish.csv")
perch <- filter(Fish, Species == "Perch")
```

```{r}
perch <- select(perch,-Species)
```

### Best Models


### Best Two regressor model
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```
The best two regressor model is height and weight because those are the highest adjusted r squared.

```{r}
perchmodel <- lm(Weight ~ Height + Width, data = perch)
summary.lm(perchmodel)
```

```{r}
pmodel <- lm(Weight ~ Height + Width + Length1 + Length2 + Length3, data = perch)
summary.lm(pmodel)
```
We used two models to figure out our Residual standard error and the adjusted r squared of both models for the first residual it is 85.17 then the second one is 87.11 for the adjusted r squared the first one is 0.94 then the second on it is 0.9372.



## Bream
```{r}
Fish <- read.csv("Fish.csv")
Bream <- filter(Fish, Species == "Bream")
```

```{r}
Bream <- select(Bream,-Species)
```
### Best Models

### Best Two regressor model
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Bream,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The best regression model is Length1 Height and Weight because it is at the top.

```{r}
Breammodel <- lm(Weight ~ Height + Width, data = Bream)
summary.lm(Breammodel)
```

```{r}
Bmodel <- lm(Weight ~ Height + Width + Length1 + Length2 + Length3, data = Bream)
summary.lm(Bmodel)
```

The first Residual standard error 53.98 the second one 53.96 the first adjusted r square is 0.9334 the adjusted r square is 0.9335



## Roach
```{r}
Fish <- read.csv("Fish.csv")
Roach <- filter(Fish, Species == "Roach")
```

```{r}
Roach <- select(Roach,-Species)
```
### Best Models

### Best Two regressor model
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

```{r}
Roachmodel <- lm(Weight ~ Height + Width, data = Roach)
summary.lm(Roachmodel)
```

```{r}
Rmodel <- lm(Weight ~ Height + Width + Length1 + Length2 + Length3, data = Roach)
summary.lm(Rmodel)
```

The first Residual standard error is 35.63 the second is 37.58 the first adjusted r square is 0.8391 the second one is 0.821.

```{r}
favstats(Weight~Species,data=Fish)
```

The Bream has a mean weight of 617.8 Which is 1.6 times bigger than the perch which has a mean weight of 382.2. The roach is smaller than both fishes and has a weight of 152. So that leaves that Bream is the heaviest fish that we have for the data.

The adjusted r squared for perch is 0.94 the standard deviation is higher than all the other fishes at 347.61 . The bream's adjusted r squared is 0.93 the standard deviation is lower than perch but still bigger than Roach.
Bream has a tighter deviation that Perch and Roach, Perch's residual standard error is 85.17  which indicates that the data is not as tight as bream, bream has a residual standard error is 53.1.

```{r}
basicCN <- ggplot(perch,aes(y=Weight,x=Length1))
```
```{r}
basicCN + geom_point() + geom_lm()
```

## Final Summary Statements


In all the test we did it showed us that for the first model the first summary was the best for the second model the second summary was the best and for the third model the first summary was the best all the summarys were focused on finding which fish weighed the most and how would we be able to mesusre it by. 
